Statistics Project

### 2022-12-10 rough_analysis.Rmd
Updated prediction models, added Kaggle scores from submitted material

backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)               #the p-values for these should be fiddled
stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)       #with to test a better selection set, although could be unnec.

@@

@@

@@

The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20

>>>>

backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)               #the p-values for these should be fiddled with, 
stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)

mystery4thsetWIP

@@

#--------------------------------------------- Backwards Elimination Prediction:

@@

#-------------------------------------------- Forwards Selection Prediction:

forward_pred = predict(forwardt1$model, test_housing)
real_forward = exp(forward_pred)
real_fp_joined = data.frame(test_housing$Id, real_forward)
real_fp_joined[is.na(real_fp_joined)]<-10000
colnames(real_fp_joined) = c("Id", "SalePrice")
write.csv(real_bp_joined, "./Kaggle_forwardt1_testset.csv", row.names = FALSE)

#-------------------------------------------- Stepwise Selection Prediction:

stepwise_pred = predict(stepwiset1$model, test_housing)
real_step = exp(stepwise_pred)
real_sp_joined = data.frame(test_housing$Id, real_step)
real_sp_joined[is.na(real_sp_joined)]<-10000
colnames(real_sp_joined) = c("Id", "SalePrice")
write.csv(real_sp_joined, "./Kaggle_stepwiset1_testset.csv", row.names = FALSE)

@@

The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20855. While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal. This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time. This should be further investigated.
